\documentclass{res}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{hidelinks}
\usepackage[symbol]{footmisc}
\renewcommand*{\thefootnote}{\fnsymbol{footnote}}

\newsectionwidth{10pt}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\newcommand{\tab}[1]{\hspace{.2\textwidth}\rlap{#1}}
\newcommand{\rfill}{\hspace*{\fill}}
\newcommand{\studentinfo}[1]{\textit{\textcolor{gray}{(#1)}}}
\newenvironment{denselist}{
    \begin{list}{\small{$\bullet$}}%
    {\setlength{\itemsep}{0ex} \setlength{\topsep}{0ex}
    \setlength{\parsep}{0pt} \setlength{\itemindent}{0pt}
    \setlength{\leftmargin}{1.5em}
    \setlength{\partopsep}{0pt}}}%
    {\end{list}}

\newcommand{\squishlist}{
   \begin{list}{$\bullet$}
    { \setlength{\itemsep}{0pt}
      \setlength{\parsep}{2pt}
      \setlength{\topsep}{0pt}
      \setlength{\partopsep}{0pt}
      \leftmargin=25pt
\rightmargin=0pt
\labelsep=5pt
\labelwidth=10pt
\itemindent=0pt
\listparindent=0pt
\itemsep=\parsep
    }
}

%\documentcliass[11pt]{article} %Sets the default text size to 11pt and class to article.
%------------------------
\setlength{\textheight}{9.5in} % increase text height to fit on 1-page
\linespread{1.15} %This controls line spacing throughout the whole document
\begin{document}
\raggedright
\centerline{\LARGE \textbf{Alan M Luu}}
\vspace{-10pt}
\noindent %Prevents the following text from being indented
\centerline{ \href{mailto:amluu94@gmail.com}{amluu94@gmail.com} $\bullet$
\href{http://alanmluu.github.io}{alanmluu.github.io}$\bullet$
 GitHub: \href{https://github.com/alanmluu}{alanmluu}}
\vspace{1pt}
 \vspace{5pt}
\begin{resume}
\vspace{-30pt}
\section{EDUCATION}
\vspace{2pt}Ph.D. Physics, University of Illinois, Urbana-Champaign\rfill Aug 2016 - Present
\vspace{2pt}
\begin{itemize}
\item Advisor: Jun S. Song
\item Specialization: Machine learning, statistics, computational biology, genomics
\end{itemize}
\vspace{-8pt}B.A. Physics, University of California, Berkeley \rfill Aug. 2012 - May 2016
\vspace{-5pt}
\section{RESEARCH EXPERIENCE}
\vspace{2pt}
\href{http://song.igb.illinois.edu/}{UIUC Computational Biology Group (Advisor: Jun Song)}  \hfill Jan 2017 - Present
\vspace{2pt}
\begin{itemize}%TODO: add description of the impact of these work
\item {\normalfont Developing novel adaptive MCMC method using Markov chain regeneration and normalizing flows to augment Hamiltonian Monte Carlo for Bayesian inference.}
\item {\normalfont Investigating relationship between T-cell receptor amino acid sequence and cutaneous T-cell lymphoma using convolutional neural networks (CNNs) and string similarity metrics.}
\item {\normalfont Performing differential expression analysis on scRNA-seq data from keratinocytes using limma and carrying out statistical analysis to implicate cell of origin and transcription factors associated with Basal and Squamous Cell Carcinomas. Publication in preparation.}
\item {\normalfont Exploring generative models of scRNA-seq data using generative adversarial networks (GANs).}
\item {\normalfont Analyzed MiSeq data using Bowtie2 and Tophat2 to quantify CRISPR-mediated base editing efficiency, exon skipping, and off-target effects using CRISPR cytidine and adenine base editors.}
\item {\normalfont Created web application to target exons  for exon skipping using CRISPR base editors.}
\end{itemize}
\href{https://www.kuehnlab.org/}{UIUC Quantitative Ecology and Evolution Lab (Advisor: Seppe Kuehn)} \hfill May 2017 - Jul. 2017
\begin{itemize}
\item {\normalfont Carried out statistical and network analysis on gene knockout data to investigate the relationship between phenotypic robustness and evolvability.}
\end{itemize}
\href{http://bionano.physics.illinois.edu/}{UIUC Computational Bio-Nano Group (Advisor: Aleksei Aksimentiev)} \hfill Sept - Dec 2016\\
%{\sl University of Illinois at Urbana-Champaign} \\
%{\normalfont Position: CPLC Fellow. Advisor: Aleksei Aksimentiev}
\begin{itemize}
\item {\normalfont Ran large molecular dynamics simulations using high performance computing resources to investigate stability of 3D nano-engineered DNA structures in various ionic solutions.}
\end{itemize}
%\href{http://research.physics.berkeley.edu/haeffner/}{UC Berkeley Ion Trap Group (Advisor: Hartmut Haeffner)} \hfill Feb 2015 - May 2016\\
%\begin{itemize}
%\item Machined fixtures to house and align optical elements on an optical table. Designed and manufactured Helmholtz coils using electromagnetic simulation tools, CAD, and 3D printing. %TODO: rewrite to remove orphan line
%\end{itemize}
\href{https://irene.lbl.gov/}{Project IRENE at Lawrence Berkeley National Laboratory (Advisor: Carl Haber)}  \hfill Jan - Oct 2014\\
\begin{itemize}
\item {\normalfont Implemented and benchmarked optical-flow-based algorithm to reconstruct audio signals from high resolution confocal microscope images of lacquer audio records.}
\end{itemize}
\vspace{-7pt}
\section{INDUSTRY EXPERIENCE}
\href{https://seyvu.ai/}{Data Scientist at Seyvu Inc.}  \hfill Apr 2018 - Present \\
\begin{itemize}
\item Analyzing large scale social media and survey data for  health insurance, food manufacturing, \\and consumer technology businesses to derive market insights.
\item Developed text analytics pipeline involving preprocessing, sentiment analysis, and time series analysis. Designed an interactive data dashboard to visualize results.
\item Devised novel \emph{aspect sentiment analysis} method using word2vec and statistical analysis.
\item Implemented document clustering visualizations based on doc2vec.
\item Created interactive word co-occurence network visualizations using Altair and Vega-Lite.

\end{itemize}
\newpage
\section{PUBLICATIONS}
\begin{itemize}[leftmargin=0in,label={}]
   % TODO: Include title and authors or In Preparation Papers
\item Jackson Winter, \textbf{Alan Luu}, Michael Gapinske, Wendy S. Woods,
Jun S. Song, Pablo Perez-Pinera. Disruption of Splice Acceptors Using CRISPR-Cas9 Adenine Base Editors Induces Exon Skipping. Under submission to \textit{Cell Discovery}.
\item Michael Gapinske\footnote{Equal Contribution}, \textbf{Alan Luu}\footnotemark[1], Jackson Winter, Wendy S. Woods, Kurt A. Kostan, Nikhil Shiva, Jun S. Song, Pablo Perez-Pinera. \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6092781/}{CRISPR-SKIP: programmable gene splicing with single base editors.
} \textit{Genome Biology}, August 2018.
\end{itemize}
\vspace{-10pt}
\section{SKILLS}
Machine Learning, Data Science, Deep Learning, Statistical Analysis, Quantitative Biology and Genomics, Sequence Analysis, Text Analytics, Natural Language Processing, Image Processing %Mathematical Proofs
\\ \textbf{Languages:} Python, R, Java, C, Matlab, Mathematica
\\ \textbf{Data Science:} Keras, TensorFlow, Jupyter, Altair, scikit-learn, pandas, Git
\\ \textbf{Computational Biology:} VMD, NAMD, FastQC, cutadapt, Bowtie2, Tophat2, HTSeq, limma
\\ \textbf{Web Development:} Flask, HTML, CSS, Javascript, MySQL, Vega-Lite
\vspace{-10pt}
\section{TEACHING}
   \textbf{University of California at Berkeley}
   \\Course Assistant: PHYS7B (Intro to Electromagnetism and Thermodynamics) \hfill June - Aug 2016
   \\Grader: PHYS137B (Advanced Quantum Mechanics)\hfill Jan - Aug 2016
   \\Grader: PHYS139 (General Relativity)\hfill Jan - Aug 2016
   \\Course Lab Assistant: CS61A (Structure and Interpretation of Computer Programs)\hfill Aug - Dec 2013
\vspace{-10pt}
\section{AWARDS}
   UIUC Center for the Physics of Living Cells Symposium Best Speaker Award \hfill Apr 2018\\
   UIUC Center for the Physics of Living Cells Fellowship \hfill Aug 2016 - Aug 2018\\
   UC Berkeley College of Letters and Science Dean's Honor List \hfill Aug 2012 - May 2014\\
   UC Berkeley Pomerantz Scholarship \hfill Aug 2014 - Aug 2015\\
   \begin{itemize}
   \item {\normalfont Awarded for high academic standing and progress in the physics major}
   \end{itemize}
   \vspace{-12pt}
   UC Berkeley Regents and Chancellor's Scholarship \hfill Aug 2012 - May 2016\\
   \begin{itemize}
   \item {\normalfont Awarded to top 1\% of applicants (top 5\% of admitted students)}
   \end{itemize}
\vspace{-10pt}
\section{SERVICE}
Lunch Coordinator and Volunteer for Society of Physics Students \rfill Aug 2013 - May 2016 \\
Campaign Organizer for California Public Interest Research Group \rfill Aug 2012 - Dec 2012 \\
\end{resume}
\end{document}
