%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\addtolength{\topmargin}{-.25in}
\addtolength{\textheight}{.5in}
\usepackage{hyperref}
\hypersetup{colorlinks,urlcolor=black}
\usepackage{enumitem}
\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage[symbol]{footmisc}

\renewcommand*{\thefootnote}{\fnsymbol{footnote}}

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Alan M. Luu} % Your name at the top

\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'

\moveleft.5\hoffset\centerline{Carl R. Woese Institute for Genomic Biology, Room 2132, 1206 W. Gregory Dr., Urbana, IL 61801} % Your address
\moveleft.5\hoffset\centerline{amluu94@gmail.com \ \ \ \ \ \ \ \ (916) 850-5841}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION}

\bf{Ph.D. Physics} \hfill Aug. 2016 - Present\\
{\sl University of Illinois at Urbana-Champaign}

\begin{itemize}
\item {\normalfont Advisor: Jun S. Song}
\end{itemize}

\bf{B.A. Physics} \hfill Aug. 2012 - May 2016 \\
{\sl University of California at Berkeley}

\begin{itemize}
\item {\normalfont GPA: 3.79}
\item {\normalfont Graduated with Distinction in General Scholarship}
\end{itemize}

\section{PUBLICATION}
\begin{itemize}[leftmargin=0in,label={}]
% TODO: Include title and authors or In Preparation Papers
\item Michael Gapinske, \textbf{Alan Luu}\footnote{Equal Contribution}, Jackson Winter, Wendy S. Woods, Kurt A. Kostan, Nikhil Shiva, Jun S. Song, Pablo Perez-Pinera, \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6092781/}{CRISPR-SKIP: programmable gene splicing with single base editors.
}. \textit{Genome Biology}, August 2018.

\end{itemize}
\section{SKILLS}

%----------------------------------------------------------------------------------------
%	RESEARCH EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{RESEARCH \\ EXPERIENCE}

Song Lab  \hfill Jan. 2017 - Present \\ {\sl University of Illinois at Urbana-Champaign}\\
{\normalfont Position: CPLC Fellow. Advisor: Jun Song}

\begin{itemize}
\item {\normalfont Analyzed MiSeq data using Bowtie2 and Tophat2 to determine feasibility of using CRISPR-mediated base editing to induce alternate splicing. }
\item {\normalfont Created web application to determine which exons of a gene can be modified to be excluded from the final transcript using CRISPR-mediated base editing.}
\item {\normalfont Implemented various machine learning algorithms to discover new lincRNA.}
\item {\normalfont Investigated using graph spectral sparsification to identify important edges in a network.}
\end{itemize}

Kuehn Lab \hfill May 2017 - Jul. 2017 \\ {\sl University of Illinois at Urbana-Champaign} \\
{\normalfont Position: CPLC Fellow. Advisor: Seppe Kuehn}

\begin{itemize}
\item {\normalfont Carried out Statistical and network analysis on gene knockout data to investigate the correlation between phenotypic robustness and evolvability.}
\end{itemize}

Aksimentiev Group \hfill Sept. 2016 - Dec. 2016\\ {\sl University of Illinois at Urbana-Champaign} \\
{\normalfont Position: CPLC Fellow. Advisor: Aleksei Aksimentiev}

\begin{itemize}
\item {\normalfont Ran large molecular dynamics simulations using high performance computing resources to investigate stability of 3D nano-engineered DNA structures in various ionic solutions.}
\end{itemize}
Ion Trap Group \hfill Feb. 2015 - May 2016\\ {\sl University of California at Berkeley} \\
{\normalfont Position: Undergraduate Researcher. Advisor: Hartmut Haeffner}

\begin{itemize}
\item {\normalfont Machined fixtures to house and align optical elements on an optical table.}
\item {\normalfont Designed and manufactured Helmholtz coils using electromagnetic simulation tools, computer aided design, and 3D printing. }
\end{itemize}

Irene Project \hfill Jan. 2014 - Oct. 2014\\ {\sl Lawrence Berkeley National Laboratory} \\
{\normalfont Position: Undergraduate Researcher. Advisor: Carl Haber}

\begin{itemize}
\item {\normalfont Implemented and benchmarked optical-flow-based algorithm to reconstruct audio signals from high resolution confocal microscope images of lacquer records.}
\end{itemize}

%----------------------------------------------------------------------------------------
%	TEACHING EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{TEACHING \\ EXPERIENCE}
Undergraduate Student Instructor \hfill Jun. 2016 - Aug. 2016\\
{\sl University of California at Berkeley} \\
{\normalfont Class: Physics 7B - Lower division electromagnetism and thermodynamics}\\
{\normalfont Professor: Mike Bloxham}

\begin{itemize}
\item {\normalfont Led discussion section, held office hours, and graded exams.}
\end{itemize}

Undergraduate Homework Grader \hfill Jan. 2016 - Aug. 2016\\
{\sl University of California at Berkeley}
\begin{itemize}
\item {\normalfont Physics 137B - Second course in undergraduate Quantum Mechanics}
\item {\normalfont Physics 139 - Undergraduate course in General Relativity}
\end{itemize}

Instructional Lab Assistant \hfill Aug. 2013 - Dec. 2013\\
{\sl University of California at Berkeley} \\
{\normalfont Class: CS61A - Structure and Interpretation of Computer Programs}\\
{\normalfont Professor: John DeNero}

\begin{itemize}
\item {\normalfont Helped run instructional lab section and held office hours}
\end{itemize}

\section{SKILLS}
\begin{itemize}
\item {\normalfont Programming Languages: C, Java, Python}
\item {\normalfont Web Applications: Python Flask, HTML, CSS, Javascript}
\item {\normalfont Software: Matlab, Labview, Mathematica, Jupyter notebooks, Autodesk 123D design, VMD, NAMD, Bowtie2, Tophat2, scikit-learn}
\item {\normalfont Operating Systems: Windows, MacOS, Linux/Unix}
\item {\normalfont Sequence data analyis}
\item {\normalfont Basic machine shop and construction skills including drill press, lathe, and 3D printing}
\item {\normalfont Basic image processing including optical flow, edge detection, and filtering}
\item {\normalfont Machine learning, quantitative and statistical analysis, mathematical proofs}
\end{itemize}

%----------------------------------------------------------------------------------------
%	SERVICE SECTION
%----------------------------------------------------------------------------------------

\section{SERVICE}

Society of Physics Students \hfill Aug. 2013 - May. 2016 \\
{\sl University of California at Berkeley} \\
{\normalfont Position: Lunch Host}
\begin{itemize}
\item {\normalfont Hosted lunch with physics professors and alumni in industry.}
\item {\normalfont Helped run SPS zone meeting hosted at UC Berkeley}
\end{itemize}

California Public Interest Research Group \hfill Aug. 2012 - Dec. 2012 \\
{\normalfont Position: Campaign Organizer}
\begin{itemize}
\item {\normalfont Helped lead campaign to petition the Berkeley City Council to denounce the Supreme Court ruling of} {\sl Citizens United v. FEC}
\end{itemize}

\section{HONORS,\\ AWARDS, \\ SCHOLARSHIPS}

Center for the Physics of Living Cells Fellowship \hfill Aug. 2016 - Aug. 2018\\
{\sl University of Illinois at Urbana-Champaign}

College of Letters and Science Dean's Honor List \hfill Aug. 2012 - May 2014\\
{\sl University of California at Berkeley}

Pomerantz Scholarship \hfill Aug. 2014 - Aug. 2015\\
{\sl University of California at Berkeley}
\begin{itemize}
\item {\normalfont Awarded for high academic standing and progress in the physics major }
\end{itemize}

Regents and Chancellor's Scholarship \hfill Aug. 2012 - May 2016\\
{\sl University of California at Berkeley}
\begin{itemize}
\item {\normalfont Awarded to top 1\% of applicants (top 5\% of admitted students)}
\end{itemize}

\end{resume}
\end{document}
